Figures

### 2016-09-25 figures/figures.rmd
new simulations

```{r load, echo = FALSE}
load("../simdata/combine_ev_LHS4.rda")
```

@@

```{r fig5, echo = FALSE, fig.width = 10, cache = TRUE,dpi = 600}
mL3 <- subset(mL2,
       !((model=="implicit" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="random" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch+epc" &
          LHSvar %in% c("rho_base","c_u_ratio")) |
         (model=="pairform" &
          LHSvar %in% c("c_u_ratio","c_e_ratio"))))
## reorder factors
mL3$LHSvar <- factor(mL3$LHSvar,
                     levels=c("Beta1","Beta3",
                              "Duration1","Duration3",
                              "c_mean_base","c_e_ratio","rho_base",
                              "c_u_ratio"),
                     labels = c("beta[P]", "beta[D]", "D[P]", "D[D]",
                                "c", "c[e]/c[w]", "rho", "c[u]/c[w]"))

>>>>

```{r load, echo = FALSE}
load("../simdata/combineResults.rda")
```

@@

```{r fig5, echo = FALSE, fig.width = 10, cache = TRUE,dpi = 600}
mL2 <- subset(mL2, !(LHSvar %in% c("kappa", "mu")))
mL3 <- subset(mL2,
       !((model=="implicit" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="random" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch+epc" &
          LHSvar %in% c("rho_base","c_u_ratio")) |
         (model=="pairform" &
          LHSvar %in% c("c_u_ratio","c_e_ratio"))))

## reorder factors
mL3$LHSvar <- factor(mL3$LHSvar,
                     levels=c("Beta1","Beta3",
                              "Duration1","Duration3",
                              "c_mean_base","c_e_ratio","rho_base",
                              "c_u_ratio"),
                     labels = c("beta[P]", "beta[D]", "D[P]", "D[D]",
                                "c", "c[e]/c[w]", "rho", "c[u]/c[w]"))
